Analysis-ready VCF at Biobank scale using Zarr

### 2025-01-23 paper.tex
Update some author details

% Middle, alphabetical order
\author[6]{Benjamin Elsworth} % https://orcid.org/0000-0001-7328-4233
\author[7,8]{Jérémy Guez} % https://orcid.org/0009-0007-6406-5187
\author[9]{Jonny Hancox} % ?
\author[10]{Ben Jeffery} % https://orcid.org/0000-0002-1982-6801
\author[7,8,11]{ Konrad J. Karczewski} % https://orcid.org/0000-0003-2878-4671
\author[12]{Alistair Miles} % https://orcid.org/0000-0001-9018-4680
\author[13]{Sam Tallman} % https://orcid.org/0000-0001-7183-6276
\author[14]{Per Unneberg} % https://orcid.org/0000-0001-5735-3315
\author[1]{Rafal Wojdyla} % https://orcid.org/0009-0005-0735-7090
\author[15]{Shadi Zabad} % https://orcid.org/0000-0002-8003-9284

@@

\affil[1]{Related Sciences}
\affil[2]{The New Zealand Institute for Plant \& Food Research Ltd, Lincoln,
New Zealand}
\affil[3]{Department of Biochemistry, School of Biomedical Sciences, University of Otago, Dunedin, New Zealand}
\affil[4]{Independent researcher}
\affil[5]{Tom White Consulting Ltd.}
\affil[6]{Our Future Health}
\affil[7]{Program in Medical and Population Genetics, Broad Institute of MIT and Harvard, Cambridge, Massachusetts 02142, USA}
\affil[8]{Analytic and Translational Genetics Unit, Massachusetts General
Hospital, Boston, Massachusetts 02114, USA}
\affil[9]{Nvidia}
\affil[10]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery, 
University of Oxford, UK}
\affil[11]{Novo Nordisk Foundation Center for Genomic Mechanisms of Disease, Broad Institute of MIT and Harvard, Cambridge, Massachusetts 02142, USA}
\affil[12]{Wellcome Sanger Institute}
\affil[13]{Genomics England}
\affil[14]{Department of Cell and Molecular Biology, National
  Bioinformatics Infrastructure Sweden, Science for Life Laboratory,
  Uppsala University, Uppsala, Sweden}
\affil[15]{School of Computer Science, McGill University, Montreal, QC, Canada}

@@

Chunk decompression comprises a significant fraction of processing 
time [FIXME crossrefs?] and host-to-GPU data transfer is 
often a bottleneck. It is therefore useful in some applications 
to directly decompress Zarr chunks into GPU memory. 
KvikIO is a Python package that provides access to optimised
GPU IO routines, and providing support for Zarr along with
access to several GPU optimised compression codecs.
To explore the performance of these codecs we recompressed
the \texttt{call\_AD} (allele depth) array
(96514, 2504, 7) [int16 more details]. In call cases it took around 1s 
to compress and store this 3.15GiB array. [Details about compression codecs?]
We then measured the time to decompress these arrays and 
copy back to host memory [Why??]. This required about 0.6s with the 
fastest codecs. For reference, using the Zstandard codec on a single
CPU thread required about 7.6s.

>>>>

% Middle, alphabetical order
\author[6]{Benjamin Elsworth} % https://orcid.org/0000-0001-7328-4233
\author[7,8]{Jérémy Guez} % https://orcid.org/0009-0007-6406-5187
\author[9]{Jonny Hancox} % https://orcid.org/0009-0003-5799-5299
\author[10]{Ben Jeffery} % https://orcid.org/0000-0002-1982-6801
\author[7,8,11]{ Konrad J. Karczewski} % https://orcid.org/0000-0003-2878-4671
\author[12]{Alistair Miles} % https://orcid.org/0000-0001-9018-4680
\author[13]{Sam Tallman} % https://orcid.org/0000-0001-7183-6276
\author[14]{Per Unneberg} % https://orcid.org/0000-0001-5735-3315
\author[1]{Rafal Wojdyla} % https://orcid.org/0009-0005-0735-7090
\author[15]{Shadi Zabad} % https://orcid.org/0000-0002-8003-9284

@@

\affil[1]{Related Sciences}
\affil[2]{The New Zealand Institute for Plant \& Food Research Ltd, Lincoln,
New Zealand}
\affil[3]{Department of Biochemistry, School of Biomedical Sciences, University of Otago, Dunedin, New Zealand}
\affil[4]{Independent researcher}
\affil[5]{Tom White Consulting Ltd.}
\affil[6]{Our Future Health, Manchester, UK.}
\affil[7]{Program in Medical and Population Genetics, Broad Institute of MIT and Harvard, Cambridge, Massachusetts 02142, USA}
\affil[8]{Analytic and Translational Genetics Unit, Massachusetts General
Hospital, Boston, Massachusetts 02114, USA}
\affil[9]{NVIDIA Ltd, Reading, UK}
\affil[10]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery, 
University of Oxford, UK}
\affil[11]{Novo Nordisk Foundation Center for Genomic Mechanisms of Disease, Broad Institute of MIT and Harvard, Cambridge, Massachusetts 02142, USA}
\affil[12]{Wellcome Sanger Institute}
\affil[13]{Genomics England}
\affil[14]{Department of Cell and Molecular Biology, National
  Bioinformatics Infrastructure Sweden, Science for Life Laboratory,
  Uppsala University, Uppsala, Sweden}
\affil[15]{School of Computer Science, McGill University, Montreal, QC, Canada}

@@

Chunk decompression comprises a significant fraction of processing 
time [FIXME crossrefs?] and host-to-GPU data transfer is 
often a bottleneck. It is therefore useful in some applications 
to directly decompress Zarr chunks into GPU memory. 
KvikIO~\cite{kvikio} is a Python package that provides access to optimised
GPU IO routines, and providing support for Zarr along with
access to several GPU optimised compression codecs.
To explore the performance of these codecs we recompressed
the \texttt{call\_AD} (allele depth) array
(96514, 2504, 7) [int16 more details]. In call cases it took around 1s 
to compress and store this 3.15GiB array. [Details about compression codecs?]
We then measured the time to decompress these arrays and 
copy back to host memory [Why??]. This required about 0.6s with the 
fastest codecs. For reference, using the Zstandard codec on a single
CPU thread required about 7.6s.
